Quantifying stochastic noise in cultured\\ circadian reporter cells

### 2015-03-16 main_text.tex
updating acknowledgement

\section*{Acknowledgments}
We thank Tsuyoshi Hirota, Eric Zhang, David Welsh, and John Abel for the helpful discussions, as well as the each of the authors of the original experiments for making their raw data available online.
This work was supported by the National Institutes of Health/National Institute of General Medical Sciences under award number 1R01GM096873-01 and by the Institute for Collaborative Biotechnologies through grant W911NF-09-0001 from the U.S.\ Army Research Office.

>>>>

\section*{Acknowledgments}
We thank Tsuyoshi Hirota, David Welsh, and John Abel for the helpful discussions, as well as the each of the authors of the original experiments for making their raw data available online.
This work was supported by the National Institutes of Health/National Institute of General Medical Sciences under award number 1R01GM096873-01 and by the Institute for Collaborative Biotechnologies through grant W911NF-09-0001 from the U.S.\ Army Research Office.
